%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.25in}
\addtolength{\evensidemargin}{-0.25in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Jonathan Lu}} & Email: \href{mailto:hijonlu@gmail.com}{hijonlu@gmail.com}\\
  {Brooklyn, NY} & Mobile: \href{tel:+17072179276}{+1-707-217-9276} \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Squarespace}{New York, NY}
      {Senior Software Engineer II}{June 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Google Domains Acquisition}
          {Led the integration of 10 million Google domains, ensuring feature parity for advanced domain configurations such as custom nameservers and DNSSEC.}
        \resumeItem{SEO Tools}
          {Partnered with OpenAI and used GPT-3.5 Turbo to design an LLM-powered content generation microservice for SEO-focused single page apps.}
        \resumeItem{Domain Search Optimization}
          {Decreased domain search latency by 60\% by rewriting ranking algorithms and simplifying legacy codepaths with Redux Toolkit.}
      \resumeItemListEnd
    \resumeSubSubheading
      {Senior Software Engineer}{December 2020 - June 2023}
      \resumeItemListStart
        \resumeItem{Universal Checkout}
          {Increased trial-to-paid plan mix of Squarespace website subscriptions by 10\% through delivering a modernized and unified checkout experience across every product (+\$2mil annual revenue in the first year).}
        \resumeItem{Frontsite Component Library}
          {Leveraged atomic design principles to set best practices for component hierarchies and effective cascading styles.}
        \resumeItem{Mobile Conversion}
          {Architected and implemented a mobile-specific onboarding flow which increased landing-to-trial by 21\% and landing-to-subscription by 27\%. }
        \resumeItem{Typescript}
          {Established developer guidelines for Typescript adoption and documentation standards.}
      \resumeItemListEnd
      \resumeSubSubheading
      {Software Engineer}{August 2018 - December 2020}
        \resumeItemListStart
          \resumeItem{Runtime Registration Forms}
            {Launched support for region-specific domain registrations such as .ca and .com.au by developing a flexible and responsive model for runtime generation of TLD-specific forms.}
          \resumeItem{Asynchronous Transfers}
            {Integrated asynchrony into the domain transfer flow to unblock customer action trapping and increase overall domain transfer success rates from 76\% to 98\%.}
        \resumeItemListEnd

% --------Multiple Positions Heading------------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 -- Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd

%-------------------------------------------

    \resumeSubheading
      {Clear Capital}{Roseville, CA}
      {Frontend Engineer}{June 2017 -- April 2018}
      \resumeItemListStart
        \resumeItem{Core Platform Rewrite}
          {Rebuilt the ClearCollateral platform using React JS alongside Redux, Node, and Express from its original PHP implementation.}
        \resumeItem{Documentation}
          {Directed and documented styling structure for app-wide UI/UX coherence among all 5 engineers in the company.}
        \resumeItem{Jest Testing}
          {Expanded test coverage by 36\% between existing and newly-added components.}
      \resumeItemListEnd

    \resumeSubheading
      {Calix Inc.}{Petaluma, CA}
      {Software Engineering Intern}{Summer 2016}
      \resumeItemListStart
        \resumeItem{Meteor.js}
          {Implemented Meteor.js clustering for load balancing alongside nginx to increase Compass resilience and scalability.}
        \resumeItem{Docker Migration}
          {Initiated a migration of critical web services to Docker to simplify deployment and upgrade processes on a cloud-based infrastructure.}
        \resumeItem{Elasticsearch optimization}
          {Boosted Elasticsearch performance by a factor of 5 through fine-tuning ngram analysis.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}{: Typescript/Javascript, LESS/CSS, HTML, Java}
    \resumeSubItem{Technologies}{: React, OpenAI, Next.js, Framer Motion, Node.js, Git, Spring Boot, GCP, Kubernetes}
    \resumeSubItem{Design Tooling}{: Figma, Rive, Illustrator, Photoshop, Kapwing}
 \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Davis}{Davis, CA}
      {B.S. in Computer Science, Minor in Design, GPA: 3.66}{September 2014 -- March 2018}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
